---
title: "Compare File List"
output: html_document
date: "2023-11-09"
---



```{r}
hdflist <- list.files(path="../2018NABorealAlbedo/",pattern='hdf$', full.names = TRUE)
```

```{r}
hdflist
```

```{r}
tiflist <- list.files(path="../outputs/2018NABorealAlbedo/",pattern='tif$', full.names = TRUE)
```

```{r}
tiflist
```


```{r}
setdiff(tools::file_path_sans_ext(basename(hdflist)), tools::file_path_sans_ext(basename(tiflist)))
```

# Trackin 2018 NA Boreal Albedo file numbers
001 - 025 236 (hdf) 235 (tif) "LC08_L1TP_033026_20180316_20180402_01_T2_albedo_broad"

026-050 - 222
051-075 - 499
076-100 - 934

total images 1162


```{r}
wsaTiflist <- list.files(path="../outputs/WSA/Batch5",pattern='tif$', full.names = TRUE)
```
```{r}
springlist <- list.files(path="../outputs/sprgWsa/",pattern='tif$', full.names = TRUE)
```

# Notes on Files that do not convert from hdf to tif by batch
## L1GT_test
297 HDF files read into list
297 tif files read into list (50.4 GB all bands | 10.4 GB 2 bands)
## Batch 3
83 hdf files read into list
82 tif files read into list ( all bands | 5.9 GB 2 bands)
"LC08_L1TP_037017_20181022_20181031_01_T1_albedo_broad"

## Batch 4
408 hdf files read into list
408 tif files read into list (153.0 GB all bands | 29.4 GB 2 bands)

## Batch 5
940 hdf files read into list
940 tif files read into list (330.5 GB all bands | 64.6 gb 2 bands)

## Batch6
764 hdf files read into list
764 tif files read into list (276.1 GB all bands | 54.3 GB 2 bands)

## Batch 7 
639 hdf files read into list
636 tif files read into list (194.0 GB all bands | 38.8 GB 2 bands)
[1] "LC08_L1TP_072018_20180909_20180913_01_T1_albedo_broad"
[2] "LC08_L1TP_072019_20180909_20180913_01_T1_albedo_broad"
[3] "LC08_L1TP_072020_20180925_20181009_01_T1_albedo_broad"

## Batch 8
269 HDF files read into list
269 TIF files read into list (74.6 GB all bands | 15.1 GB 2 bands)

## Batch 9
2 hdf files read into list
2 tif files read into list (267.3 MB all bands | 63.8 mb 2 bands)

##j01m03_1
681 hdf
681 tif (385.1 GB | 71.5 GB)

##j01m03_2
318 hdf
318 tif (174.1 GB |  GB)

##j01m03_3
605 hdf
605 tif (174.1 GB |  GB). 143.7 gb for all spring images


